Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-01-13 lloveras_2020_Albert_Section4.tex
mergeo nuevo

\subsection{\albert{DEMT Reconstructions}}\label{demt}

@@

\subsection{\albert{AWSoM Simulations}}\label{awsom}

@@

\subsection{\albert{Tracing Results Along Magnetic Fieldlines}}\label{trace}

@@

\albert{To determine} the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid. Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = r{\rm d}\theta/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point. In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, for a total of $96,000$ starting points.

\albert{For analysis purposes, the geometry of all traced magnetic field lines is classified. They are first classified as open or closed according to their full geometry. Each closed magnetic field line is further classified as ``small" or ``large", according to its coronal length $L$ being smaller or larger than the median value ${\rm Md}(L)$ of the whole population, respectively. This median value is ${\rm Md}(L)=0.51$ and $0.46\,\mrsun$ for CR-2082 and CR-2208, respectively. Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints (i.e. their location at $r=1\,\mrsun$) to its apex (i.e., the location of maximum height).} \notebyalbert{Diego, aquí ordené y corregí mucho y creo que es un buen ejemplo de corrección de estilo de redacción, si querés comparar con como estaba antes. Nota: MHD no tiene source surface! Ahora bien, además informo ${\rm Md}(L)$. Para ello multipliqué por dos el valor mediano de las longitudes de las piernas (que recuerdo de memoria, por ahí la pifié). Vale la pena que le muestres estos histogramas a Fede y la pieza de código de donde sale, para confirmar la metodología y de paso los números. Es importante.}

At this stage, all DEMT and AWSoM products, electron density and \albert{temperature} in particular, can be traced along open and closed magnetic field lines. Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one). To each sample point, the results corresponding to the tomographic voxel where it is located are assigned to it. As a result, for each field line one data point per tomographic cell \albert{is obtained. This approach} was firstly used by \citet{huang_2012} to \albert{study temperature} structures in the solar minimum \albert{corona and by} \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.

For each open field line and \albert{for each closed field leg}, an exponential fit \albert{was applied} to the electron density \albert{data points} and a linear fit applied to the electron temperature \albert{data points}. For \albert{the DEMT model} the data points used were $\sqravgN(r)$ and $\Tm(r)$, and in case of \albert{the AWSoM models} the data points used were $\Ne(r)$ and $\Te(r)$. The exponential and linear fit equations are described by

@@

\notebyalbert{Este párrafo debe ser movido al menos aquí (estaba más abajo), pues el siguiente párrafo ya utiliza el concepto up/down. Además está corregido.} \albert{Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies. As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop. Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}. In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and considering time-averaged heating rates.}

\notebyalbert{Reordené y corregí mucho el siguiente párrafo. Lo que see lee es correcto en cada detalle y palabra? Está bien explicado todo lo que concierne a chi-suqared? La jerga estadística es precisa y correcta (no confundir confidence level con confidence interval, está bien?}
\albert{To determine if a traced filed line leg is of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$ data points. We then select field lines for which the temperature increases or decreases significantly with height by requiring $|\rhoTr| > 0.5$. We then measure the quality of the linear fit to the temperature-height data by means of a chi-squared test \citep{recipes}, and select legs for which the fit has a 90\% confidence level. In this way, legs for which the DEMT temperature does not show a significant variation with height, or the linear fit to temperature is good enough, are not considered in this analysis. Finally, selected legs are then classified as up or down according to if $\rhoTr > +0.5$ or $\rhoTr < -0.5$, respectively. The linear fit allows characterization of the variation of $\Tm$ with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg. Both fits consider tomographic systematic uncertainty of the electron temeprature and density, respectively estimated to be $\Delta(\Tm) \approx 0.07\,\MK$ and $\Delta(N_e)\approx 4.0\times 10^6\,\cm^{-3}$ by \citet{lloveras_2017}. \notebyalbert{No comprendo bien si esta última linea está bien ubicada aquí, de todas formas lo corregí un poco. Precisaría que discutamos los tres estos tres párrafos en naranja el lunes.} In summary, to be selected a leg must meet all three following conditions:}

\begin{enumerate}
\item 
The leg must go through at least five tomographic grid cells with reconstructed data, and there must be at least one data point in each third of the range of heights spanned by the leg. \albert{This requirement is set to ensure a reasonably spread sample of heights along the leg.}
\item 
The \albert{DEMT temperature and height data points must meet} $|\rhoTr| > 0.5$.
\item 
\albert{The condifence level of both the exponential and linear fits must be larger than 90\%.} \notebyalbert{Aquí corregí, está bien expresado?}
\end{enumerate}

@@

\albert{
\begin{itemize}
\item Type 0: closed-small-down with footpoints in the range $|{\rm latitude}|<50\mdeg$. 
\item Type I: closed-small-up with footpoints in the range $|{\rm latitude}|<50\mdeg$. 
\item Type II: closed-large-up with footpoints in the range $|{\rm latitude}|>40\mdeg$. 
\item Type III: open with footpoint in the range $|{\rm latitude}|>60\mdeg$.
\end{itemize}
}

In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed. \albert{As shown below, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}

\subsection{\albert{Energy Input Flux}}\label{energia}

@@

\albert{The high temperature of the corona requires heating mechanisms to compensate for the the losses. While the vast majority of the existing literature on coronal heating focuses on ARs, some studies have been dedicated to the heating of quiet-Sun regions. In particular,  \citet{maccormack_2017} developed a new application of the DEMT technique to estimate the energy input flux required at the base of quiet-Sun coronal loops to mantain them stable. The technique is based on tracing the DEMT results along field lines of a global coronal magnetic model, just as described in the previous Section \ref{trace}.}

\albert{Consider} a simple energy balance for each magnetic flux tube, \albert{in which the dominating losses of} radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated \albert{by a} coronal heating power($E_h$) \citep{aschwanden_2004}:

@@

\noindent
where $s$ is the position along \albert{the flux tube} and the \albert{power quntities} are in units of $[{\rm erg\,sec^{-1}\,cm^{-3}}]$.

@@

{For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met. Open legs are indicated in gray color and closed ones in black color. For each leg, the fits to tomografic temperature and density were applied, as given by Equations (\ref{Nfit})-(\ref{Tfit}). Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} Of the 48000 legs selected for CR-2082, 21\% are type 0, 31\% are type I, 22\% are type II and 26\% type III. On the other hand, of the 57000 legs selected for CR-2208, 9\% are type 0, 36\% are type I, 26\% are type II and 29\% type III. \notebyalbert{Luego de des-ralear, las piernas seleccionadas en Figura 4 eran del orden de 100 mil, para  ambas rotaciones. Algo no está consistente aquí.}

@@

\begin{table}[h!]
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
\hline
Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
\hline
0    & 1&24 &(\Mi&19\%)  &   \albert{\bf 7}&\albert{\bf 1} &(\Pl&~3\%) &   1&09 &(\Pl&24\%) \\
I    & 1&15 &(\Mi&10\%)  &   7&5 &(\Pl&29\%) &   1&25 &(\Pl&24\%) \\
II   & 0&98 &(\Mi&20\%)  &   9&9 &(\Pl&19\%) &   1&36 &(\Pl&16\%) \\
III  & 0&65 &(\Mi&15\%)  &   7&6 &(\Pl&12\%) &   0&97 &(\Pl&~7\%) \\
\hline          
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.}
\label{tabla_demt}
\end{table}

@@

{A comparison of the results between the two rotations shows that, compared to CR-2082, target rotation CR-2208 was characterized by \albert{$\approx 10-20\%$} lower values of the electron density at the coronal base, $\approx 5-30\%$ larger values of density scale height, and \albert{$\approx 5-25\%$} larger values of the electron temperature.}

@@

{{Adding the} radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}. Note that for type 0 loops there is a marginal population characterized by the unphysical result $\phi_h<0$. As shown by \citet{maccormack_2017}, {this affects only the smallest sized loops of the type 0}, and it is {most probably} due to the limited temperature sensitivity of the instrumental passbands. The radiative loss term is {here calculated based on plasma emission detected by three coronal bands of EUVI or AIA. Though accounting for most of the coronal plasma, there surely is additional emission out of the instrumental sensitivity range. As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, \albert{being characterized by $\phi_c<0$. \vfill}} % NOTA el vfill

\subsection{\albert{Comparison of the DEMT and AWSoM Models}}\label{awsom_res}

@@

To characterize the results of the AWSoM model in distinct magnetic structures, its results for electron density and temperature were traced along its magnetic field lines. For each field line leg, the results were then fit to Equations (\ref{Nfit}) and (\ref{Tfit})\albert{, considering only data points above heliocentric height $1.055\,\mrsun$. We then classified the traced legs into types I, II and III, according to the criteria described in Section \ref{trace}.  Legs of type 0 are not included for AWSoM, as in its current implementation it can not simulate down loops, a point we will discuss in the next section.}

@@

{For the two target rotations, Table \ref{tabla_comp} summarizes a quantitative comparative analysis between the results of the DEMT and AWSoM models \albert{based on the results shown in Figures \ref{histos_2082} and \ref{histos_2208}}. The DEMT results are expressed as absolute values, while the ASWSoM results are informed as a percentual variation relative to the corresponding result for DEMT. The following major results can be drawn.}

@@

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
\hline
Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
\hline
CR-2082\\
I    & 1&15 &(\Mi&14\%)  &   7&5 &(\Pl&~8\%) &   1&25 &(\Mi&\albert{\bf 10}\%) \\
II   & 0&99 &(\Mi&25\%)  &   \albert{\bf 9}&9 &(\Mi&~2\%) &   1&36 &(\Mi&~2\%) \\
III  & 0&65 &(\Mi&15\%)  &   7&6 &(\Mi&~8\%) &   0&97 &(\Mi&~9\%) \\
\hline          
CR-2208\\
I    & 1&03 &(\Pl&~6\%)  &   9&7 &(\Mi&~8\%) &   1&55 &(\Mi&17\%) \\
II   & 0&79 &(\Pl&~9\%)  &  11&8 &(\Mi&14\%) &   1&58 &(\Mi&~8\%) \\
III  & 0&55 &(\Pl&~\albert{\bf 2}\%)  &   8&6 &(\Mi&16\%) &   1&04 &(\Mi&11\%) \\
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.}
\label{tabla_comp}
\end{table}

@@

\section{\albert{Discussion and Conclusions}}\label{discu}

>>>>

\subsection{{DEMT Reconstructions}}\label{demt}

@@

\subsection{{AWSoM Simulations}}\label{awsom}

@@

\subsection{{Tracing Results Along Magnetic Fieldlines}}\label{trace}

@@

{To determine} the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid. Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = r{\rm d}\theta/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point. In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, for a total of $96,000$ starting points.

{For analysis purposes, the geometry of all traced magnetic field lines is classified. They are first classified as open or closed according to their full geometry. Each closed magnetic field line is further classified as ``small" or ``large", according to its coronal length $L$ being smaller or larger than the median value ${\rm Md}(L)$ of the whole population, respectively. This median value is \diego{${\rm Md}(L)=0.50$} and $0.46\,\mrsun$ for CR-2082 and CR-2208, respectively. Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints (i.e. their location at $r=1\,\mrsun$) to its apex (i.e., the location of maximum height).} \notebyalbert{Diego, aquí ordené y corregí mucho y creo que es un buen ejemplo de corrección de estilo de redacción, si querés comparar con como estaba antes. Nota: MHD no tiene source surface! Ahora bien, además informo ${\rm Md}(L)$. Para ello multipliqué por dos el valor mediano de las longitudes de las piernas (que recuerdo de memoria, por ahí la pifié). Vale la pena que le muestres estos histogramas a Fede y la pieza de código de donde sale, para confirmar la metodología y de paso los números. Es importante.}

At this stage, all DEMT and AWSoM products, electron density and {temperature} in particular, can be traced along open and closed magnetic field lines. Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one). To each sample point, the results corresponding to the tomographic voxel where it is located are assigned to it. As a result, for each field line one data point per tomographic cell {is obtained. This approach} was firstly used by \citet{huang_2012} to {study temperature} structures in the solar minimum {corona and by} \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.

For each open field line and {for each closed field leg}, an exponential fit {was applied} to the electron density {data points} and a linear fit applied to the electron temperature {data points}. For {the DEMT model} the data points used were $\sqravgN(r)$ and $\Tm(r)$, and in case of {the AWSoM models} the data points used were $\Ne(r)$ and $\Te(r)$. The exponential and linear fit equations are described by

@@

\notebyalbert{Este párrafo debe ser movido al menos aquí (estaba más abajo), pues el siguiente párrafo ya utiliza el concepto up/down. Además está corregido.} {Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies. As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop. Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}. In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and considering time-averaged heating rates.}

\notebyalbert{Reordené y corregí mucho el siguiente párrafo. Lo que see lee es correcto en cada detalle y palabra? Está bien explicado todo lo que concierne a chi-suqared? La jerga estadística es precisa y correcta (no confundir confidence level con confidence interval, está bien?}
{To determine if a traced filed line leg is of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$ data points. We then select field lines for which the temperature increases or decreases significantly with height by requiring $|\rhoTr| > 0.5$. \diego{hablemos sobre esta frase} We then measure the quality of the linear fit to the temperature-height data by means of a chi-squared test \citep{recipes}, and select legs for which the fit has a 90\% confidence level. In this way, legs for which the DEMT temperature does not show a significant variation with height, or the linear fit to temperature is good enough, are not considered in this analysis. Finally, selected legs are then classified as up or down according to if $\rhoTr > +0.5$ or $\rhoTr < -0.5$, respectively. The linear fit allows characterization of the variation of $\Tm$ with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg. Both fits consider tomographic systematic uncertainty of the electron temeprature and density, respectively estimated to be $\Delta(\Tm) \approx 0.07\,\MK$ and $\Delta(N_e)\approx 4.0\times 10^6\,\cm^{-3}$ by \citet{lloveras_2017}. \notebyalbert{No comprendo bien si esta última linea está bien ubicada aquí, de todas formas lo corregí un poco. Precisaría que discutamos los tres estos tres párrafos en naranja el lunes.} In summary, to be selected a leg must meet all three following conditions:}

\begin{enumerate}
\item 
The leg must go through at least five tomographic grid cells with reconstructed data, and there must be at least one data point in each third of the range of heights spanned by the leg. {This requirement is set to ensure a reasonably spread sample of heights along the leg.}
\item 
The {DEMT temperature and height data points must meet} $|\rhoTr| > 0.5$.
\item 
{The condifence level of both the exponential and linear fits must be larger than 90\%.} \notebyalbert{Aquí corregí, está bien expresado?}\diego{si!}
\end{enumerate}

@@

{
\begin{itemize}
\item Type 0: closed-small-down with footpoints in the range $|{\rm latitude}|<50\mdeg$. 
\item Type I: closed-small-up with footpoints in the range $|{\rm latitude}|<50\mdeg$. 
\item Type II: closed-large-up with footpoints in the range $|{\rm latitude}|>40\mdeg$. 
\item Type III: open with footpoint in the range $|{\rm latitude}|>60\mdeg$.
\end{itemize}
}

In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed. {As shown below, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}

\subsection{{Energy Input Flux}}\label{energia}

@@

{The high temperature of the corona requires heating mechanisms to compensate for the the losses. While the vast majority of the existing literature on coronal heating focuses on ARs, some studies have been dedicated to the heating of quiet-Sun regions. In particular,  \citet{maccormack_2017} developed a new application of the DEMT technique to estimate the energy input flux required at the base of quiet-Sun coronal loops to mantain them stable. The technique is based on tracing the DEMT results along field lines of a global coronal magnetic model, just as described in the previous Section \ref{trace}.}

{Consider} a simple energy balance for each magnetic flux tube, {in which the dominating losses of} radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated {by a} coronal heating power($E_h$) \citep{aschwanden_2004}:

@@

\noindent
where $s$ is the position along {the flux tube} and the {power quntities} are in units of $[{\rm erg\,sec^{-1}\,cm^{-3}}]$.

@@

{For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met. Open legs are indicated in gray color and closed ones in black color. For each leg, the fits to tomografic temperature and density were applied, as given by Equations (\ref{Nfit})-(\ref{Tfit}). Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} Of the 48000 legs selected for CR-2082, 21\% are type 0, 31\% are type I, 22\% are type II and 26\% type III. On the other hand, of the 57000 legs selected for CR-2208, 9\% are type 0, 36\% are type I, 26\% are type II and 29\% type III. \notebyalbert{Luego de des-ralear, las piernas seleccionadas en Figura 4 eran del orden de 100 mil, para  ambas rotaciones. Algo no está consistente aquí.}\diego{Statloop 6 alturas noda algo asi como 150k piernas, algunas no se trazan (entre 30 y 40k) lo cual nos deja aprox 110k. SUpongo que te quedaste con ese numero. Pero elimino los cuasi isotermicos, perdemos 30k en el streamer y 10k en CH. Luego hacemos una seleccion qie involucra footpoints y ahi perdemos lo que falta! Es decir, el numero del draft ya es des-raleado.}

@@

\begin{table}[h!]
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
\hline
Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
\hline
0    & 1&24 &(\Mi&19\%)  &   {\bf 7}&{\bf 1} &(\Pl&~3\%) &   1&09 &(\Pl&24\%) \\
I    & 1&15 &(\Mi&10\%)  &   7&5 &(\Pl&29\%) &   1&25 &(\Pl&24\%) \\
II   & 0&98 &(\Mi&20\%)  &   9&9 &(\Pl&19\%) &   1&36 &(\Pl&16\%) \\
III  & 0&65 &(\Mi&15\%)  &   7&6 &(\Pl&12\%) &   0&97 &(\Pl&~7\%) \\
\hline          
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.}
\label{tabla_demt}
\end{table}

@@

{A comparison of the results between the two rotations shows that, compared to CR-2082, target rotation CR-2208 was characterized by {$\approx 10-20\%$} lower values of the electron density at the coronal base, $\approx 5-30\%$ larger values of density scale height, and {$\approx 5-25\%$} larger values of the electron temperature.}

@@

{{Adding the} radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}. Note that for type 0 loops there is a marginal population characterized by the unphysical result $\phi_h<0$. As shown by \citet{maccormack_2017}, {this affects only the smallest sized loops of the type 0}, and it is {most probably} due to the limited temperature sensitivity of the instrumental passbands. The radiative loss term is {here calculated based on plasma emission detected by three coronal bands of EUVI or AIA. Though accounting for most of the coronal plasma, there surely is additional emission out of the instrumental sensitivity range. As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, {being characterized by $\phi_c<0$. \vfill}} % NOTA el vfill

\subsection{{Comparison of the DEMT and AWSoM Models}}\label{awsom_res}

@@

To characterize the results of the AWSoM model in distinct magnetic structures, its results for electron density and temperature were traced along its magnetic field lines. For each field line leg, the results were then fit to Equations (\ref{Nfit}) and (\ref{Tfit}){, considering only data points above heliocentric height $1.055\,\mrsun$. We then classified the traced legs into types I, II and III, according to the criteria described in Section \ref{trace}.  Legs of type 0 are not included for AWSoM, as in its current implementation it can not simulate down loops, a point we will discuss in the next section.}

@@

{For the two target rotations, Table \ref{tabla_comp} summarizes a quantitative comparative analysis between the results of the DEMT and AWSoM models {based on the results shown in Figures \ref{histos_2082} and \ref{histos_2208}}. The DEMT results are expressed as absolute values, while the ASWSoM results are informed as a percentual variation relative to the corresponding result for DEMT. The following major results can be drawn.}

@@

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
\hline
Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
\hline
CR-2082\\
I    & 1&15 &(\Mi&14\%)  &   7&5 &(\Pl&~8\%) &   1&25 &(\Mi&{\bf 10}\%) \\
II   & 0&99 &(\Mi&25\%)  &   {\bf 9}&9 &(\Mi&~2\%) &   1&36 &(\Mi&~2\%) \\
III  & 0&65 &(\Mi&15\%)  &   7&6 &(\Mi&~8\%) &   0&97 &(\Mi&~9\%) \\
\hline          
CR-2208\\
I    & 1&03 &(\Pl&~6\%)  &   9&7 &(\Mi&~8\%) &   1&55 &(\Mi&17\%) \\
II   & 0&79 &(\Pl&~9\%)  &  11&8 &(\Mi&14\%) &   1&58 &(\Mi&~8\%) \\
III  & 0&55 &(\Pl&~{\bf 2}\%)  &   8&6 &(\Mi&16\%) &   1&04 &(\Mi&11\%) \\
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.}
\label{tabla_comp}
\end{table}

@@

\section{{Discussion and Conclusions}}\label{discu}
